---
output: github_document
bibliography: references.bib
---

```{r, include = FALSE}
library(mlr3misc)
library(utils)
library(mlr3tuningspaces)
source("R/bibentries.R")
writeLines(toBibtex(bibentries), "references.bib")

lgr::get_logger("mlr3")$set_threshold("warn")
lgr::get_logger("bbotk")$set_threshold("warn")
set.seed(1)
options(datatable.print.class = FALSE, datatable.print.keys = FALSE)
```

# mlr3tuningspaces

Package website: [release](https://mlr3tuningspaces.mlr-org.com/)

<!-- badges: start -->
[![tic](https://github.com/mlr-org/mlr3tuningspaces/workflows/tic/badge.svg?branch=main)](https://github.com/mlr-org/mlr3tuningspaces/actions)
[![CRAN Status](https://www.r-pkg.org/badges/version-ago/mlr3tuningspaces)](https://cran.r-project.org/package=mlr3tuningspaces)
[![StackOverflow](https://img.shields.io/badge/stackoverflow-mlr3-orange.svg)](https://stackoverflow.com/questions/tagged/mlr3)
[![Mattermost](https://img.shields.io/badge/chat-mattermost-orange.svg)](https://lmmisld-lmu-stats-slds.srv.mwn.de/mlr_invite/)
<!-- badges: end -->

Collection of search spaces for hyperparameter tuning.
Includes various search spaces that can be directly applied to an `mlr3` learner.
Additionally, meta information about the search space can be queried.
Tuning spaces by @bischl_2021 and @kuehn_2018.

## Installation

Install the last release from CRAN:

```{r eval = FALSE}
install.packages("mlr3tuningspaces")
```

Install the development version from GitHub:

```{r eval = FALSE}
remotes::install_github("mlr-org/mlr3tuningspaces")
```

## Example

```{r, include = FALSE}
# mute load messages
library(mlr3tuningspaces)
library(data.table)
```

### Quick Tuning


A learner passed to the `lts()` arguments the learner with the default tuning space from

```{r}
library(mlr3tuningspaces)

# tune learner with default search space
instance = tune(
  method = "random_search",
  task = tsk("pima"),
  learner = lts(lrn("classif.rpart")),
  resampling = rsmp ("holdout"),
  measure = msr("classif.ce"),
  term_evals = 10
)

# best performing hyperparameter configuration
instance$result
```

### Tuning Search Spaces



```{r, message = FALSE}
library("data.table")

# print keys and learners
as.data.table(mlr_tuning_spaces)

# get tuning space and view tune token
tuning_space = lts("classif.rpart.default")
tuning_space$values

# get learner with tuning space
learner = tuning_space$get_learner()

# tune learner
instance = tune(
  method = "random_search",
  task = tsk("pima"),
  learner = learner,
  resampling = rsmp ("holdout"),
  measure = msr("classif.ce"),
  term_evals = 10)

instance$result
```

### Adding New Tuning Spaces

We are looking forward to new collections of tuning spaces from peer-reviewed articles.
You can suggest new tuning spaces in an issue or contribute a new collection yourself in a pull request.
Take a look at an already implemented collection e.g. our [default tuning spaces](https://github.com/mlr-org/mlr3tuningspaces/blob/main/R/tuning_spaces_default.R) from @bischl_2021.
A `TuningSpace` is added to the ` mlr_tuning_spaces` dictionary with the  `add_tuning_space()` function.
Create a tuning space for each variant of the learner e.g. for `LearnerClassifRpart` and `LearnerRegrRpart`.

```{r, eval=FALSE}
vals = list(
  minsplit  = to_tune(2, 64, logscale = TRUE),
  cp        = to_tune(1e-04, 1e-1, logscale = TRUE)
)

add_tuning_space(
  id = "classif.rpart.example",
  values = vals,
  tags = c("default", "classification"),
  learner = "classif.rpart",
  label = "Classification Tree Example"
)
```

Choose a name that is related to the publication and adjust the documentation.

The reference is added to the `bibentries.R` file

```{r, eval=FALSE}
bischl_2021 = bibentry("misc",
  key           = "bischl_2021",
  title         = "Hyperparameter Optimization: Foundations, Algorithms, Best Practices and Open Challenges",
  author        = "Bernd Bischl and Martin Binder and Michel Lang and Tobias Pielok and Jakob Richter and Stefan Coors and Janek Thomas and Theresa Ullmann and Marc Becker and Anne-Laure Boulesteix and Difan Deng and Marius Lindauer",
  year          = "2021",
  eprint        = "2107.05847",
  archivePrefix = "arXiv",
  primaryClass  = "stat.ML",
  url           = "https://arxiv.org/abs/2107.05847"
)
```

We are happy to help you with the pull request if you have any question.

## References
